---
title: "hardcorexgamerxsephirophxd"
output: html_notebook
---


Finding the objectively best word for wordle because video games:
https://www.powerlanguage.co.uk/wordle/

word list obtained using:
https://www.pcmag.com/how-to/want-to-up-your-wordle-game-the-winning-word-is-right-on-the-

general info on the most common letters:
https://www3.nd.edu/~busiforc/handouts/cryptography/letterfrequencies.html

Let's load in the wordbank from the game. I've pre-removed all the non-letter things in the file but if you want the raw file is there too :)

remove hash symbol if you have not installed tidyverse before.

```{r}
#install.packages("tidyverse")

library(tidyverse)

wordbank <- read.delim("./data/wordle_list.txt", header = F)
wordbank <- tolower(wordbank)
```

And separate into characters to count the most common letters

```{r}
wordbank <- str_split(wordbank[1], pattern = "")
table <- as.data.frame(table(wordbank))
table <- table[4:30, ] #remove the non-letters that were somehow left in
table
```

Initial Conclusions:

Top letters differ a little from the most common letters in the dictionary, likely because wordle only uses 5 letter words.

Funnily enough, "AROSE" is a better word than "ARISE" in the wordle meta.

Next Steps: consider that words can have reocurring letters. So for example parry would only count as one use of R instead of two.